\documentclass[12pt,oneside,final]{thesis}
\usepackage{latexsym}
\usepackage{amsmath,amsfonts}
\usepackage{graphicx}
\usepackage{fixltx2e}
\usepackage{wrapfig}
\usepackage{fancyhdr}    % Use nice looking headers along with the required footer page numbers
\usepackage{xspace}
\usepackage{url}
\usepackage{rotating} % for rotating column header titles
\usepackage{multirow} % for multirow cells in tables
\usepackage{hhline} % allows cleaner double horizontal lines (where the vertical lines cut through)
\usepackage[round]{natbib} % allows citet and citep

%\usepackage[colorlinks,plainpages=false]{hyperref} % for links to figures, tables, sections, and references (from Zhifei/Arnab)
                                                  %%% (comment out above line for submission as it must be all black
                                                  %%%  ALSO comment out the spacing adjustment below)

% Needed for the bibliography
\def\newblock{\hskip .11em plus .33em minus .07em} 
%Define the header/footer style
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{15pt}
\lhead{\leftmark}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0pt}
\fancypagestyle{plain}{% Redefine ``plain'' style for chapter boundaries
\fancyhf{} % clear all header and footer fields
\fancyfoot[C]{\thepage} % except the center
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}}

\newcommand{\argmax}[1]{\underset{#1}{\operatorname{argmax}}}

\usepackage{color}

\newcommand{\remove}[1]{}
%\newcommand{\Note}[1]{}
\newcommand{\Note}[1]{\textbf{\large\textcolor{blue}{[#1]}}}
\newcommand{\NoteJS}[1]{\Note{#1~--JS}}

\begin{document}

\title{Parallel Sentence Discovery for Low-Resource Languages}

\author{Jason R. Smith}
\degreemonth{May}
\degreeyear{2013}
\dissertation
\doctorphilosophy
\copyrightnotice

\maketitle

\begin{abstract}
Statistical machine translation (SMT) accuracy depends crucially on training
data in the form of parallel corpora---bilingual documents that are direct
translations of each other. Most easily accessible parallel corpora originate
from government and news sources, covering a limited set of languages and
domains. To expand coverage, we can discover parallel sentences in comparable
corpora---bilingual documents about the same topic that are not direct
translations. Though comparable corpora are extremely varied, we can exploit
their lexical and structural cues to extract parallel sentences that improve machine
translation. We demonstrate this on three representative parallel corpora: the
Web, Twitter, and Wikipedia. We show in each case how their unique structure
reveals signals that can be exploited to discover parallel sentences cheaply and
effectively. We estimate how much data can be found by language pair and domain,
and we show that the discovered parallel data substantially improves SMT
performance, especially for languages and domains with low coverage.

% Web
The Web is the by far the largest source of comparable data, containing
trillions of words and constantly growing. The greatest challenge in mining the
Web is accessing and searching over this massive amount of data.
We use Amazon's Elastic MapReduce and 
Common Crawl, a publicly available web crawl, to scale up a previous mining
approach \citep{Resnik03} to 32 terabytes of webpages. 
%To do this affordably, we use simple URL matching
%heuristics to find parallel webpages, then apply the STRAND algorithm
%\citep{Resnik03} to matching webpage pairs.
We mine 386
million tokens of parallel data for 18 language pairs in about 24 hours for under \$500.
The data we extracted improves SMT performance by
0.5 BLEU on news domain test sets for several language pairs,
and by up to 5.0 on open domain test sets for Spanish-English.

% Twitter
For an enormous, unaligned collection of documents like the Web, simple
heuristics are sufficient for extracting large amounts of parallel data. When we
move to smaller, more structured datasets, we can afford to take advantage of
that structure. The next source of data we investigate is
Twitter, a microblogging service where users post tweets (140 character
messages) to their followers. Parallel data on Twitter may arise intentionally
from bilingual users tweeting the same content in two languages, or incidentally
from different users referencing the same current event. 
We analyze several potential signals for finding parallel data: hashtags, user
mentions, authors, and URLs.
We use these signals to align potentially parallel tweets, and apply a
supervised classifier to determine which pairs are actually parallel.

% Wiki
Some comparable corpora have stronger indicators of where parallel data can be
found.
Wikipedia, a multilingual online encyclopedia, is attractive as a
comparable corpus because articles on the same topic are linked across languages. However,
the articles are not parallel since they are rarely created by direct translation.
We develop a novel sentence alignment model for these comparable article pairs which is able to
capture document structure, allowing it to improve over the baseline which
classifies sentence pairs independently. We extract parallel data for Spanish,
German, and Bulgarian (paired with English), and see BLEU improvements of up to
10 points on test sets created from Wikipedia.

The data we collected from the Web, Twitter, and Wikipedia substantially improves SMT
performance across several languages and domains. We see especially large improvements
when testing on domains with low coverage.
We not only find large amounts of parallel data across many
language pairs and domains, we also release this data as a resource
to the SMT community. Our Web data has already been used as part of the training
sets for the Workshop on Statistical Machine Translation.
\end{abstract}

\setcounter{chapter}{0}
\include{chapter01-intro}

\setcounter{chapter}{1}
\include{chapter05-web}

\setcounter{chapter}{2}
\include{chapter02-supervised}

\setcounter{chapter}{3}
\include{chapter03-unsup}

\setcounter{chapter}{4}
\include{chapter04-related_work}

%\setcounter{chapter}{4}
%\include{chapter05-web}

% TODO: Remove this in the final version
%\setcounter{chapter}{5}
%\include{scraps}

% TODO: Switch back to IEEE for final submission
%\bibliographystyle{IEEEtran}
\bibliographystyle{plainnat}
\bibliography{refs}

\end{document}
